### 2022-11-09 NSF2022/Description/backgroundv2.tex
background mods

We look for $N_b$-many rigid body transformations
\begin{equation}
\label{eq:RBT}
F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{equation}
where $i = 1,\ldots,N_b,$
$R_i(t)$ is a rotation (proper orthogonal) $n \times n$ matrix,
$\aa_i(t)$ are the granule centers, and $\XX$ is a reference coordinate.
The transformations \eqref{eq:RBT} tell us how the granules move through space
and we use the shape and
boundary conditions for $U_i$ to capture the local
properties of the suspended media e.g., lipids, peptides, Janus spheres.
Throughout, $\nu$ refers to unit normal pointing into $\Omega(t)$ (Figure \ref{fig:flow_map}).

The key idea is to define the dynamics using the following
boundary value problem system:
\begin{alignat}{4}
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  && \nabla \cdot \uu = 0, && \quad \xx \in \Omega(t), \label {eqn:stokes} \\
  \label{eqn:phase}
  -\rho^2 \Delta \eta + f'(\eta) &= 0, && &&\quad \xx \in \Omega(t),\\
\label{eqn:noslip}        
\uu(\xx) &= \frac{dF_i}{dt}(\XX,t)
&&=\vv_i + \omega_i \times (\xx - \aa_i), 
&&\quad \xx \in \Gamma_i(t),\\
\label{eqn:material}
\eta(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$
and where $\xx = F_i(\XX,t)$.
Finally,
\begin{equation}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left[\mu(\nabla \uu + \nabla \uu^T + pI) + T_i\right]\nnu \,\dif s = \mathbf{0},\quad
\end{equation}
where
\begin{equation}
\label{eqn:hydro_stress}
T_i = -\rho^{-1} f'(\eta)I
  + \rho\left(\tfrac{1}{2}|\nabla \eta|^2I - \nabla \eta \nabla
  \eta^T\right)
\end{equation}
for the identity matrix $I$.

The above form a semi-linear elliptic 
system for evolution of the granules.  Equation~\eqref{eqn:stokes} is the
Stokes equations that describes the velocity $\uu$ and pressure $p$ of
the viscous aqueous phase.  Equation~\eqref{eqn:phase} describes the
phase transitions of the scalar order parameter $\eta$ with a decay
length $\rho$. Mathematically, this order parameter is responsible for
the attraction and adhesion between granules that want to align boundaries
of like phase.

The next three equations are the moving domain boundary conditions.
Equations~\eqref{eqn:noslip} specify a no-slip
boundary condition for a rigid body with translation velocity $\aa'_i(t) = \vv_i$
and angular velocity $\omega_i$
about the point $\aa_i(t) \in U_i(t)$.
($\omega_i$ is the axial vector of the
skew symmetric matrix $R'_i(t)$.)
In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phases at water-granule interface.
In other words, the boundary condition for $\eta$ is transported by the flow.
Finally,
equation~\eqref{eqn:stressbalance} closes the system by requiring that
the hydrodynamic stress is balanced by the phase stress $T_i$ in
\eqref{eqn:hydro_stress}.

We call the rigid bodies $U_i(t)$ granules since they are small, compact
parcels of a suspended medium, e.g. lipids, Janus spheres.
We have departed from the terminology ``particles'' here
to emphasize the role played by their finite size. 
In our simulations
(see section \ref{sec:specific_aim1}),
we include a finite length repulsion to avoid particle
collisions.

Intriguingly, the
formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} captures
exactly the right behavior expected from amphiphilic self-assembly.
For example, three bodies with amphiphilic label
(see section \ref{sec:specific_aim1}) spontaneously
self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure \ref{fig:flow_map}).
Moreover, a simple change of boundary conditions from
amphiphilic, to biased hydrophobic, to polar results in distinct
equilibrium morphologies (Figure~\ref{fig:self-assembly2}).

@@

The system~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} has an elegant
mathematical structure. In terms of locally in time well-posedness,
given disjoint granules with sufficiently smooth boundaries and data, the
system always has a solution and these solutions have a locally
Lipschitz dependence on the particle centers and orientations.
Solutions of~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} obey the
energy law
\begin{align}
  F = \int_{\Omega_t}
  \left(\rho |\nabla \eta|^2 + \rho^{-1} f(\eta)\right) \,d\xx,
  \quad
  \frac{d}{dt}F
  = - \int_{\Omega_t} \left(\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2\right) \,d\xx.
\end{align}
Mathematically, this energy law states that the free energy $F$ of the
water order phase transitions, which depends on the granule
configurations, is lost due to hydrodynamic dissipation. It is evident
that minimizers of the functional $F$ are unique and satisfy the
Euler-Lagrange equation~\eqref{eqn:phase}. There is a subtlety in the
energy law, though. Namely, the time derivative of the free energy $F$
also involves the moving boundary, accounted for by the Rayleigh
Transport Theorem, and the fact that the boundary data for $\eta$ are
transported by the rigid body motion. In fact, the water order surface
stress $T_i$ is the variational derivative that shows up in this
calculation.

\begin{figure}[t!]
\begin{center}
\includegraphics[width=\textwidth]{figures/Background/coarsening.pdf}
\end{center}
\caption{\label{fig:coarsening}}
\end{figure}
The model has a broad range of applicability to self-organization
phenomena in chemistry and biological physics. Since the formulation is
scale independent, it can represent a suspension of amphiphiles, where
the granules represent the mean properties of a small collection of
lipids, at the nanoscopic scale. For larger scales, the representation
is literal and the granules Janus spheres. The proposal deals with the
physical origins in section ().

To summarize, the
formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} shares a lot
of the features in phase field modeling, with the big exception that the
free energy depends on the granule configurations, rather than phase field
function. To make an explicit connection though, we can consider a phase
field model where one ``fluid'' phase instantaneously reaches minimality
while the other ``solid'' phase moves to further decrease free energy.
The model is also closely related to a recent and strongly developing
direction studying colloids immersed in nematic liquid crystals. As is
the case for nematics, it is natural to understand what is the effect of
the flow in such a context, but a first step is to obtain some solid
well-posedness results. The proposal discusses some mathematical
generalizations in section ().

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral formulation}
\label{sec:bie}

>>>>

We look for $N_b$-many rigid body transformations
\begin{equation}
\label{eq:RBT}
F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{equation}
where $i = 1,\ldots,N_b,$
$R_i(t)$ is a rotation (proper orthogonal) $n \times n$ matrix,
$\aa_i(t)$ are the granule centers, and $\XX$ is a reference coordinate.
The transformations \eqref{eq:RBT} tell us how the granules move through space.
Throughout, $\nu$ refers to unit normal pointing into $\Omega(t)$ (Figure \ref{fig:flow_map}).

The key idea is to define the dynamics using the following
boundary value problem system:
\begin{alignat}{4}
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  && \nabla \cdot \uu = 0, && \quad \xx \in \Omega(t), \label {eqn:stokes} \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && &&\quad \xx \in \Omega(t),\\
\label{eqn:noslip}        
\uu(\xx) &= \frac{dF_i}{dt}(\XX,t)
&&=\vv_i + \omega_i \times (\xx - \aa_i), 
&&\quad \xx \in \Gamma_i(t),\\
\label{eqn:material}
\phi(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$
and where $\xx = F_i(\XX,t)$.
Finally,
\begin{equation}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{equation}
where
\begin{equation}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = -\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)
\end{equation}
are the hydrodynamic and phase stresses, respectively; 
$I$ is the $n\times n$ identity matrix.
For vectors $\aa, \bb \in \mathbb{R}^2$,
we follow the usual convention of defining
the ``cross product'' as
$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$
where $\kk = (0,0,1) \in \mathbb{R}^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.

The above form a semi-linear elliptic 
system for evolution of the granules.  Equations~\eqref{eqn:stokes} are the
Stokes equations that describes the velocity $\uu$ and pressure $p$ of
the viscous aqueous phase.  Equation~\eqref{eqn:phase} describes the
phase transitions of the scalar order parameter $\phi$ with a decay
length $\epsilon$.
The scalar function $W(\phi)$ is a well potential where the local 
minimima representing low energy states of the water phase.
Mathematically, this order parameter is responsible for
the attraction and adhesion between granules that want to align boundaries
of like phase.

The next three equations are the moving domain boundary conditions.
Equations~\eqref{eqn:noslip} specify a no-slip
boundary condition for a rigid body with translation velocity $\aa'_i(t) = \vv_i$
and angular velocity $\omega_i$
about the point $\aa_i(t) \in U_i(t)$.
($\omega_i$ is the axial vector of the
skew symmetric matrix $R'_i(t)$.)
In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phases at water-granule interface.
The boundary condition for $\phi$ is transported by the flow
and satisfies $\phi_t + \uu \cdot \nabla \phi = 0$ on $\Gamma_i$.
Finally,
equation~\eqref{eqn:stressbalance} closes the system by
requiring that the force and torque generated by 
hydrodynamic stress balances that generated by phase stress $T_i$ in
\eqref{eqn:hydro_stress}.

We call the rigid bodies $U_i(t)$ granules since they are small, compact
parcels of a suspended media, e.g. lipids, Janus spheres.
We use the shape and boundary conditions for $U_i$ to capture the local
properties of the suspended media. 
We have departed from the terminology ``particles'' here
to emphasize the role played by their finite size. 
In our simulations (see section \ref{sec:specific_aim1}),
we include a finite length repulsion to avoid particle
collisions.

The system~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
has the energy law
\begin{equation}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega_t}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{equation}
Here $E$ is the energy stored in the phase transitions.
Because $E$ depends both on $\phi$ and $\Omega(t)$,
the derivation of \eqref{eq:energy_law}
is somewhat subtle and has been worked out in detail in \cite{Fu2018_SIAM}.
It goes as follows.
Using the Rayleigh Transport Theorem, 
the time derivative out $E$ yields an energy
density flux involving the phase stress $T_i$
at the boundary, plus a bulk term involving 
the Euler-Lagrange derivative of $E.$
The Euler-Lagrange derivative vanishes due to~\eqref{eqn:phase}
and the boundary flux transforms into viscous dissipation due to 
\eqref{eqn:hydro_stress} and the Stokes equations.

Mathematically, a change in granule configuration
instantaneously changes the phase energy $E$
the dynamics are such that energy is lost due to hydrodynamic dissipation.
Further details and generalizations are provided in
the Specific Aim 1 section \ref{sec:specific_aim1}.

The model has a broad range of applicability to self-organization
phenomena in chemistry and biological physics. For one,
the formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures
exactly the right behavior expected from amphiphilic self-assembly.
For example, three bodies with amphiphilic label
(see section \ref{sec:specific_aim1}) spontaneously
self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure \ref{fig:flow_map}).
Moreover, a simple change of boundary conditions from
amphiphilic, to biased hydrophobic, to polar results in distinct
equilibrium morphologies (Figure~\ref{fig:self-assembly2}).
Since the formulation is
scale independent, it can represent a suspension of amphiphiles, where
the granules represent the mean properties of a small collection of
lipids, at the nanoscopic scale. For larger scales, the representation
is literal and the granules Janus spheres. The proposal deals with the
physical origins in section ().
\todo[inline]{
List applications; don't forget Bertozzi.}

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[width=\textwidth]{figures/Background/coarsening.pdf}
\end{center}
\caption{\label{fig:coarsening}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral formulation}
\label{sec:bie}
